---
title: "Propensity Score-Integrated Kaplan-Meier (PSKM) Method for Single-Arm Studies"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Propensity Score-Integrated Kaplan-Meier (PSKM) Method for Single-Arm Studies}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, eval=T, echo=FALSE}
require(psrwe)
set.seed(1000)
```

# Introduction

In the **psrwe**, PS-integrated Kaplan-Meier (PSKM) method is also
implmeneted for leveraging real-world evidence in single-arm studies.
While the PSKM is an non-parametric approach for time-to-event endpoints.
Similar with the PSPP and PSCL approaches,
the PS-integrated parts `psrwe_est()` and `psrwe_borrow()`
below estimate PS model, set borrowing parameters, and deterime
discounting parameters for borrowing information.

```{r, eval=T, echo=TRUE}
data(ex_dta)
dta_ps <- psrwe_est(ex_dta,
                    v_covs = paste("V", 1:7, sep = ""),
                    v_grp = "Group",
                    cur_grp_level = "current",
                    nstrata = 5,
                    ps_method = "logistic")
ps_bor <- psrwe_borrow(dta_ps,
                       total_borrow = 30,
                       method = "distance")
```

# PS-integrated Kaplan-Meier approach for single arm studies

For single arm studies when there is one external data source, the function
`psrwe_survkm()` allows one to conduct the survival (KM) analysis proposed in
Chen et. al. (2022).
The PSKM approach is applied in each PS stratum to obtain stratum-specific
KM estimates, which are combined to complete the overal survival estimates.
Suppose we are interested in the survival probability at one year, then
we may use the argument `pred_tp=365` (days) in the function
`psrwe_survkm()`.

```{r, eval=T, echo=TRUE}
rst_km <- psrwe_survkm(ps_bor,
                       pred_tp = 365,
                       v_time  = "Y_Surv",
                       v_event = "Status")
rst_km
```

The `pred_tp_365` will be carried on to other down-stream analysis.
Howerver, the function `psrwe_survkm()` will still return results on
all distinctive time points which may be also needed for down-stream analysis
(e.g., visualizing KM curves and confidence intervals).
Therefore, the returned object `rst_km` above may have different
data structure then those retruned by the PSPP and PSCL approaches.

Note two Jackknife options have been implemented for estimating standard
errors of the survival estimates which can be the options for the
function `psrwe_survkm()`.
The `stderr_method = "jk"` applies Jackknife by each stratum and
the `stderr_method = "jkoverall"` applies Jackknife on the overall
survival probability.
Both results may be similar but slightly different
since the overall weights are fixed and close to one over the
number of total strata.

The overall survival estimates can be further visualized as below.

```{r, echo=TRUE, fig.width=6, fig.height=5}
plot(rst_km)
```

```{r, echo=TRUE, fig.width=6, fig.height=5}
plot(rst_km, add_ci = FALSE, add_stratum = TRUE)
```

```{r, echo=TRUE, fig.width=6, fig.height=5}
plot(rst_km, conf_type = "plain")
```

# PSKM inference for single arm studies

The inference for the parameters of interest such as survival
probability or rate at one year (`pred_tp=365` days) can be
further arrived from the utilitiez function `psrwe_outana()`.
For example, the code below test the one year survival probability
is `greater` than `mu = 0.7` (i.e., `70%`) or not.

```{r, eval=T, echo=TRUE}
oa_km <- psrwe_outana(rst_km, mu = 0.70, alternative = "greater")
oa_km
print(oa_km, show_details = TRUE)
summary(oa_km, pred_tps = c(180, 365))
```

# Demo example

The full example for the PSKM single-arm study can be found via
the script `demo("sec_4_4_ex", package = "psrwe")`.
Note that Jackknife standard error may take a while to finish.


# Reference

Chen, W.-C., Lu, N., Wang, C., Li, H., Song, C., Tiwari, R., Xu, Y., and
Yue, L.Q. (2022).
Propensity Score-Integrated Approach to Survival Analysis: Leveraging External
Evidence in Single-Arm Studies.
Journal of Biopharmaceutical Statistics, 32(3), 400-413.

